ClaTex: LaTeX as a Service on the Cloud

### 2017-04-06 paper.tex
windows update

>>>>

\subsection{AET Theory}
The eviction algorithm used by cache system is usually Least Recently Used (LRU). According to LRU algorithm, cache miss and cache hit both cause the cache block to move no matter how the cache is organized, LRU priority list or LRU stack\cite{Jo2013Efficient}. AET model relates to the average eviction time of cache block. Cache block may be reused several times before it is evicted. the eviction time is the time between the last access and eviction.

AET model is build on the probability of the cache block movement. $AET(c)$ is the Average Eviction Time for all data evictions in a fully associative LRU cache of size c. Suppose $Tm$ is the average time a cache block moves to position $m$. Apparently $T0$ = 0 and $AET(c) = Tc$. Suppose $rt(t)$ is the reuse numbers of reuse time t and n is the total access number. Using $f(t)$ to represent the ratio of the access number with reuse time t. $f(t) = \frac{rt(t)}{n}$. Using $P(t)$ to represent the probability of reuse time that greater than or equal to t. $P(t) = \sum\nolimits_{x \geq t}f(x)$. The movement of cache block is related to the probability $P(t)$. Suppose a cache block is in position $m$. It will move to the next position $m + 1$ if the next access data's reuse time is greater than $Tm$ whose probability is $P(Tm)$. Using another word, the speed of cache block in position m($v(Tm)$) is exactly equals to $P(T_m)$. Since the integration of the speed will be the distance, we will get the following equation.
\begin{equation}\label{eq1}
\int_{0}^{AET(c)}v(t)dt=\int_{0}^{AET(c)}P(t)dt=c
\end{equation}
Given a cache of size c, according to \ref{eq1}, we can conduct MRC if we know the probability distribution of $P(t)$. $MRC(c) = P(AET(c))$. The probability of the access whose reuse time is greater than average eviction time of the cache is also this cache's miss ratio.
